Errata

### 2025-04-06 tex/Introduction.tex
Add auxiliary files for Methodology and Results_Discussion chapters
- Created Methodology.aux with references, labels, and citations for chapter 2.
- Created Results_Discussion.aux with references, labels, and citations for chapter 3.
- Updated table and figure references for improved organization and clarity.

The influence of climate extends beyond the purely abiotic realm, shaping the composition and activity of microbial communities that inhabit the soil \citep{Nemergut2005}. Different climatic conditions select for distinct microbial populations, influencing their functional capabilities and the biogeochemical processes they mediate \citep{Newsham2016}. For instance, arid environments, characterized by low precipitation and high temperatures, harbor specialized microbial communities adapted to these extreme conditions \citep{Pearce2012}. These microbial communities play a vital role in initial soil formation and nutrient cycling, even in the face of resource scarcity \citep{Bernhard2018}. Our own studies in the Chilean Coastal Range revealed distinct patterns in soil properties and microbial communities along a climate gradient (Bernhard et al., 2018). Interestingly, these trends often followed specific, rather than homogeneous, patterns, indicating the presence of threshold processes and buffering mechanisms in soil ecosystems \citep{Bernhard2018}.

>>>>

The influence of climate extends beyond the purely abiotic realm, shaping the composition and activity of microbial communities that inhabit the soil \citep{Nemergut2005}. Different climatic conditions select for distinct microbial populations, influencing their functional capabilities and the biogeochemical processes they mediate \citep{Newsham2016}. For instance, arid environments, characterized by low precipitation and high temperatures, harbor specialized microbial communities adapted to these extreme conditions \citep{Pearce2012}. These microbial communities play a vital role in initial soil formation and nutrient cycling, even in the face of resource scarcity \citep{Bernhard2018}. Our own studies in the Chilean Coastal Range revealed distinct patterns in soil properties and microbial communities along a climate gradient \citep{Bernhard2018}. Interestingly, these trends often followed specific, rather than homogeneous, patterns, indicating the presence of threshold processes and buffering mechanisms in soil ecosystems \citep{Bernhard2018}.
